Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-24 articles/cycle/alps-cycle.tex
Update parameter table to alpine set-up.

    \begin{table*}
      \caption{%
        Parameter values used in the ice sheet model.}
      \label{tab:params}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{llrll}
        \toprule

@@

        $A_{\mathrm{c}}$   & Ice hardness coefficient cold
                & $3.61\e{-13}$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $A_{\mathrm{w}}$   & Ice hardness coefficient warm
                & $1.73\e3$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $Q_{\mathrm{c}}$   & Flow law activation energy cold
                & $6.0\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $Q_{\mathrm{w}}$   & Flow law activation energy warm
                & $13.9\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Paterson.Budd.1982} \\

@@

        $v_{\text{th}}$& Pseudo-plastic threshold velocity
                & 100.0
                & \unit{m\,a^{-1}}
                & \citet{Aschwanden.etal.2013} \\

        $c_0$   & Till cohesion
                & 0.0
                & Pa
                & \citet{Tulaczyk.etal.2000} \\

@@

        $W_{\text{max}}$ & Maximal till water thickness
                & 2.0
                & m
                & \citet{Bueler.Pelt.2015} \\

        $b_0$   & Altitude of max. friction angle
                & 0
                & m
                & -- \\

        $b_1$   & Altitude of min. friction angle
                & 200
                & m
                & \citet{Clague.1981} \\

        $\phi_0$& Minimum friction angle
                & 15
                & \degree
                & -- \\

        $\phi_1$& Maximum friction angle
                & 45
                & \degree
                & -- \\

@@

        $q_{\mathrm{G}}$   & Geothermal heat flux
                & 70.0
                & \unit{mW\,m^{-2}}
                & -- \\

@@

        $k_{\mathrm{b}}$   & Bedrock thermal conductivity
                & 3.0
                & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
                & -- \\

@@

        $D$     & Lithosphere flexural rigidity
                & $5.0\e{24}$
                & \unit{N}
                & \citet{Lingle.Clark.1985} \\

@@

        $F_{\mathrm{s}}$   & Degree-day factor for snow
                & $3.04\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Shea.etal.2009} \\

        $F_{\mathrm{i}}$   & Degree-day factor for ice
                & $4.59\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Shea.etal.2009} \\

>>>>

    \begin{table*}
      \caption{%
        Parameter values used in the ice sheet model.
        \idea{If I need to re-run all simulations, we could rethink bedrock,
              lithosphere and PDD parameters.}}
      \label{tab:params}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{llrll}
        \toprule

@@

        $A_{\mathrm{c}}$   & Ice hardness coefficient cold
                & $2.847\e{-13}$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Cuffey.Paterson.2010} \\

        $A_{\mathrm{w}}$   & Ice hardness coefficient warm
                & $2.356\e{-2}$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Cuffey.Paterson.2010} \\

        $Q_{\mathrm{c}}$   & Flow law activation energy cold
                & $6.0\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Cuffey.Paterson.2010} \\

        $Q_{\mathrm{w}}$   & Flow law activation energy warm
                & $11.5\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Cuffey.Paterson.2010} \\

        $E_{\text{SIA}}$   & SIA enhancement factor
                & 5
                & --
                & \citet{Cuffey.Paterson.2010} \\

        $E_{\text{SSA}}$   & SSA enhancement factor
                & 1
                & --
                & \citet{Cuffey.Paterson.2010} \\

@@

        $v_{\text{th}}$& Pseudo-plastic threshold velocity
                & 100
                & \unit{m\,a^{-1}}
                & \citet{Aschwanden.etal.2013} \\

        $c_0$   & Till cohesion
                & 0
                & Pa
                & \citet{Tulaczyk.etal.2000} \\

@@

        $\phi$  & Till friction angle
                & 30
                & \degree
                & \citet{Cuffey.Paterson.2010} \\

        $W_{\text{max}}$ & Maximum till water thickness
                & 2
                & m
                & \citet{Bueler.Pelt.2015} \\

@@

@@

        $k_{\mathrm{b}}$   & Bedrock thermal conductivity
                & 3
                & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
                & -- \\

@@

        $D$     & Lithosphere flexural rigidity
                & $5\e{24}$
                & \unit{N}
                & \citet{Lingle.Clark.1985} \\

@@

        $F_{\mathrm{s}}$   & Degree-day factor for snow
                & $3.297\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Huybrechts.1998} \\

        $F_{\mathrm{i}}$   & Degree-day factor for ice
                & $8.791\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Huybrechts.1998} \\

        $R$     & Refreezing fraction
                & 0.0
                & --
                & -- \\
